\documentclass[10pt]{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{enumitem}
\usepackage{nopageno}
%\usepackage{charter}  %果果推荐的衬线字体
\usepackage[usenames]{color}
\usepackage[colorlinks,
            linkcolor=black,
            urlcolor=black,
            anchorcolor=black,
            ]{hyperref}
\usepackage{lettrine}
\usepackage{fix-cm}

%\leftmargin=0.25in
%\oddsidemargin=0.25in
%\textwidth=6.0in
%\topmargin=-0.5in
%\textheight=9.75in

\leftmargin=0.25in
\oddsidemargin=0.25in
\textwidth=6.2in
\topmargin=-1.0in
\textheight=11in

%\leftmargin=0.25in
%\oddsidemargin=0.25in
%\textwidth=6.1in
%\topmargin=-0.8in
%\textheight=10.5in

\raggedleft
%\raggedright
%\setlength{\parindent}{0em}

\pagenumbering{arabic}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }
% DEFINITIONS FOR RESUME

\newenvironment{changemargin}[2]{%
  \begin{list}{}{%
    \setlength{\topsep}{0pt}%
    \setlength{\leftmargin}{#1}%
    \setlength{\rightmargin}{#2}%
    \setlength{\listparindent}{\parindent}%
    \setlength{\itemindent}{\parindent}%
    \setlength{\parsep}{\parskip}%
  }%
  \item[]}{\end{list}
}

\newcommand{\lineover}{
	\begin{changemargin}{-0.05in}{-0.05in}
		\vspace*{-8pt}
		\hrulefill \\
		\vspace*{-2pt}
	\end{changemargin}
}

\newcommand{\header}[1]{
	\begin{changemargin}{-0.7in}{-0.65in}
%	\begin{changemargin}{-0.5in}{-0.5in}
		\scshape{\large{#1}}\\
  	\lineover
	\end{changemargin}
}

\newcommand{\contact}[5]{
	\begin{changemargin}{-0.5in}{-0.5in}
		\begin{center} %flushright
			{\huge \scshape {#1}}\\ \smallskip
			\url{#2}\\ \smallskip 
			\href{mailto:#3}{#3}\\ \smallskip
			{#4}\\ \smallskip
			{#5}\smallskip
		\end{center}
	\end{changemargin}
}

\newenvironment{body} {
	\vspace*{-16pt}
	\begin{changemargin}{-0.65in}{-0.62in}
%	\begin{changemargin}{-0.4in}{-0.5in}
		%修改日志2015/11/
		%08changemargin
  }	
	{\end{changemargin}
}	

\newcommand{\school}[4]{
	\textbf{#1} \hfill \emph{#2\\}
	#3\\ 
	#4\\
}

\newcommand{\contactx}[5]{
		\begin{changemargin}{-0.8in}{-0.94in}
%	\begin{changemargin}{-0.75in}{-0.85in}
		\noindent \lettrine[lines=4]{
			\smallskip \fontsize{32}{32}\selectfont \scshape{#1}}{}
	\end{changemargin}
	\begin{changemargin}{-0.5in}{-0.6in}
			\begin{flushright} 
				{#2}\\ \smallskip
				\href{mailto:#3}{#3}\\ \smallskip
				\url{#4}\\ \smallskip
				\url{#5}\\ \smallskip
				%{#5}\smallskip
			\end{flushright}
	\end{changemargin}
}

% END RESUME DEFINITIONS
\begin{document}

\contactx{Yao Xie}{(+1) 310-923-5967}{allenshieh88@gmail.com}{allenshieh.github.io}{https://www.linkedin.com/in/yaoxieallen}

%\header{Objective}

%\begin{body}
%\vspace{14pt}
%Looking for 2018 summer Software Engineer Intern.
%\end{body}
\smallskip
\vspace{-4pt}

\header{Education}

\begin{body}
	\vspace{14pt}

	\textbf{The University of California, Los Angeles (UCLA)}, Los Angeles, CA \hfill \emph{Sep. 2017 - Present}{} \\
	\emph{M.S. in Computer Science}, GPA: \textbf{4.0}/4.0 \\
	
%	\textbf{Shanghai Jiao Tong University (SJTU)}   \hfill \emph{{Sep.}~2012 -  {Jun.}~2016 (Expected)}{} \\
%	B.S. in Information Engineering, School of Electronic Information and Electrical Engineering (SEIEE)\\
%	GPA: Major \textbf{3.77}/4.0 (\textbf{89.15}/100), Overall \textbf{3.70}/4.0 (\textbf{87.69}/100) ~~~~~~Ranking: \textbf{13}/162\\
	
	\vspace{4pt}
	\textbf{Shanghai Jiao Tong University (SJTU)}, Shanghai, China \hfill \emph{Sep. 2013 - Jun. 2017}{} \\
	\emph{B.S. in Computer Science}, GPA: \textbf{3.83}/4.3, \textit{Teaching Assistant} of Data Structure Course \\
	
%	\emph{B.S. in Information Engineering}, GPA: Core 3.77/4.0 (89.15/100), Overall 3.70/4.0 (87.69/10
	
%	\textbf{University of Cambridge} \hfill \emph{{Jan.}~2015 -  {Feb.}~2015}{} \\
%	Cambridge Academic Development Seminar -- Engineering, The Excellence Scholarship (Top 10\%)
	
\end{body}

\smallskip
\vspace{-4pt}

\header{Technical Skills}

\begin{body}
	\vspace{14pt}
	\textbf{Programming Languages:\hspace{10pt}}C/C++, C\#, Python, JAVA, MATLAB, \LaTeX, SQL\\
	\textbf{Platforms:\hspace{85pt}}Windows, Linux, Visual Studio, Android Studio\\
	
\end{body}

\smallskip
\vspace{-4pt}

\header{Internship}

\begin{body}
	\vspace{14pt}
	
	\textbf{Microsoft, APGC CSS} \hfill \emph{Jun.~2016 - Sep.~2016} \\
	\textit{Support Engineer Intern} 
	\vspace*{-5pt}
	\vspace*{2pt}
	\begin{itemize} \itemsep -0pt		
		
		\item Provided technical solutions to Microsoft core product System Center Configuration Manager by debugging, log tracing, and error reproducing.
		\item Created reports using SQL in Visual Studio for personnel information retrieval.
		\item Won $1^{st}$ place (Project Mr. Chorder) in Microsoft Young Hackathon at Shanghai site.
	\end{itemize}


\end{body}

\smallskip
\vspace{-8pt}

\header{Projects}

\begin{body}
	\vspace{14pt}
	
	\textbf{High-definition Video Wireless Transmission Optimization (C++, MATLAB, Python)} \hfill \emph{Apr.~2017 - Jun.~2017}
	\vspace*{-5pt}
	\begin{itemize} \itemsep -0pt		
		
		\item Developed an optimal relay location algorithm using Tensor Recovery in MATLAB for high-definition video wireless transmission where obstructions exist.
		\item Implemented a three-end system on three laptops (sender, relay, receiver) using C++ and a Python-controlled Roomba iRobot for real-life application.
		\item Achieved up to 5 times better performance in relay quality, stability than traditional solutions, and demonstrated the ability to environment adjustment.
	\end{itemize}
	
	\vspace{-2pt}
	
	\textbf{Mr. Chorder, A Music File-to-Score Transformer (C\#)} \hfill \emph{Aug.~2016}
	\vspace*{-5pt}
	\begin{itemize} \itemsep -0pt		
		
		\item Implemented the music score prediction module using Decision Tree (a machine learning method).
		\item Implemented a PDF render library for music scores using iTextSharp.
	\end{itemize}
	
	\vspace{-2pt}	
	
	\textbf{Video Based Multi-Object Tracking System (MATLAB)}\hfill \emph{Oct.~2015 - Dec.~2015}\\
%	\textbf{Cuisine Categorization based on Recipe Ingredients (Python)}\\
%	\textbf{Data mining theory and application}\\
	\vspace*{-5pt}
	\begin{itemize} \itemsep -0pt		
	  
      \item Developed a software system that could track multiple people in videos, and output the marked videos.
      \item Implemented modules for user registration/login, video analysis, video save/review.
      
%	\item Solved multi-label classification problem (cuisine categorization based on recipe ingredients) with xxx model and hyper-parameter tuning.
	\end{itemize}
	
	\vspace{-2pt}

	\textbf{Android Based Car Controlling (JAVA)} \hfill \emph{Oct.~2015 - Dec.~2015}
	\vspace*{-5pt}
	\begin{itemize} \itemsep -0pt		
		
	\item Developed an android application that could control the movement of a toy car through Bluetooth.
	\item Implemented multiple controlling methods, such as voice recognition (using iFLYTEK Open Platform speech technology), screen gesture, gravity (using Gyro/Acceleration sensors).		
	\end{itemize}
\vspace{-2pt}
%还需要充实充实！
%\textbf{Parkour Game Development Based on Artificial Intelligence (C++)} \hfill \emph{Sep.~2015 -  Dec.~2015}\\
%\vspace*{-5pt}
%\begin{itemize} \itemsep -0pt
	%		\item Designed and built an original parkour game by \textit{Cocos2d-x} and \textit{Visual Studio} in C++.
%	\item Built a parkour game by Cocos2d-x; designed and drew game scenes, characters' images and animation.
%	\item Implemented Artificial Intelligence module with Behavior Tree, applied Game Theory to optimize difficulty level.
	%		\item Draw game scenes and characters' images by \textit{AI} and \textit{PS}, build animation by \textit{Maya}.
	%	\item (Left for further work.)
	
%\end{itemize}  

%	\vspace{-2pt}

	\textbf{Game 2048, New Version of A Mobile Game (C++)} \hfill \emph{Jul.~2014 - {Aug.}~2014}\\
	\vspace*{-5pt}
	\begin{itemize} \itemsep -0pt 
		\item Implemented a desktop verision of the popular mobile game 2048 from scratch.
		\item Implemented additional functions, such as music/theme changing, alternative modes, etc.
	\end{itemize} 
	

	
\end{body}

\smallskip
\vspace{-8pt}

\header{Publications}

\begin{body}
	\vspace{14pt}
	
\textbf{Paper: Yao Xie}, Xiao-Yang Liu, Linghe Kong, Fan Wu, Guihai Chen, Athanasios V. Vasilakos, \textit{"Drone-Based Wireless Relay using Online Tensor Update"}, IEEE International Conference on Parallel and Distributed Systems (\textbf{ICPADS}), 2016.\\
\textbf{Patent}: Linghe Kong, \textbf{Yao Xie}, Fan Wu, Yifeng Cao, Xiao-Yang Liu, Guihai Chen, \textit{"Drone-Based Optimal Relay Locating Method and System"}, public, China, 2016.

\end{body}

\smallskip
\smallskip
\vspace{-8pt}

\header{Honors \& Awards}

\begin{body}
	\vspace{14pt}

	Excellent Graduate of SJTU\hfill \emph{Jun. 2017}\\
%	\smallskip
	
	CCF Certified Software Professionals (Top 3.61\%)\hfill \emph{Sep. 2015}\\

%	\smallskip

	Meritorious Winner (acceptance 9\%), Mathematical Contest in Modeling  \hfill  \emph{Apr. 2015}\\
%	\smallskip
	
	Scholarship for Academic Excellence, SJTU \hfill \emph{Nov. 2014, 2015, 2016}\\
	
%	\smallskip
	Arawana Scholarship (total 30 students at SJTU) \hfill \emph{Nov. 2014}
	

\end{body}


\end{document}
